Vv caluclator

### 2023-02-10 code/processing_code/vp_copies_calculator.qmd
Made edits to Vp as well
Now i no longer need to alter any raw data

Libraries
```{r}
library(tidyverse)
library(here)
```

Load data
```{r}
sq <-read_csv(here("data", "raw_data", "vp_qPCR.csv")) 
```
Filter for HEX dye (samples). Cy5 is for IAC
```{r}
sq2<- sq %>% 
  select(filter_amt,SQ, Sample, Fluor) %>%
  filter(Fluor %in% "HEX")

@@

SQ --> Copies/mL
```{r}
copies<- sq2 %>%
    mutate(
    #log_sq = ((Cq-36.114)/-3.3844), #Equation of the line to get log(SQ)
    #sq = 10^log_sq, #Unlog 
    copies_rxn = SQ*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *1, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor)%>%

  select(Sample,copies_mL)
```

Create Site Column from Sample Name 
```{r}
copies2<- copies %>%
  mutate(site = substr(copies$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)
```

Change NA to 0 and drop STD CRV NAs
```{r}
copies3<- copies2 %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))  #Dropping NAs from STD Curve
```
*Dropping NAs got rid of BO completely*

Take the average of qPCR triplicates 
```{r}
copies4<- copies3 %>% group_by(site, Sample) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() #Ungroup to spit everything back out

@@

Save as RDS and manually add date in excel
```{r}
write.csv(copies4, file= here("data","processed_data","vp_clean_copies.csv"))
```

>>>>

*This dataset is Daily Vv qPCR*

Libraries
```{r}
library(tidyverse)
library(here)
library(ggpubr)
```

Load data
```{r}
sq <-read_csv(here("data", "raw_data", "vp_run_TX_Dust_2_3_23 -  Quantification Summary.csv")) 
```

Filter for HEX dye (samples). Cy5 is for IAC
```{r}
sq2<- sq %>% 
  select(SQ,Cq, Sample, Fluor) %>%
  filter(Fluor %in% "HEX")

@@

Create Site Column from Sample Name 
```{r}
site<- sq2 %>%
  mutate(site = substr(sq2$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)
```

Add Dilution Column and Filter column
```{r}
dilution<- site%>%
  mutate(dilution = case_when(site == "BO"~"10",
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution))

filter<- dilution %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt))

@@

Cq --> Copies/mL
```{r}
copies<- filter %>%
   mutate(
   #log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
   # sq = 10^log_sq, #Unlog 
    copies_rxn = SQ*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

select(Sample,copies_mL,site)

Replace NaN with 0 for copies/mL
```{r}
replace<- copies %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))   #Dropping NAs from STD Curve 
```

Date Column
```{r}
date<- replace %>%
  mutate(day = substr(replace$Sample,4,5)) %>% #Creates new column `date` 
  mutate(date = case_when(day == "7"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day == "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day == "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day == "19"~"2022-07-19"))

Take the average of qPCR triplicates 
```{r}
final<- date %>% 
  group_by(site, Sample,date) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() %>% #Ungroup to spit everything back out 
  select(date,copies_mL,site)
```

Save as RDS and manually add date in excel
```{r}
#stop() #Write error so it wont overwrite
write.csv(final, file= here("data","processed_data","vp_clean_copies.csv"))
```

### 2023-02-10 code/processing_code/vv_copies_calclulator.qmd
Made edits to Vp as well
Now i no longer need to alter any raw data

Create Site Column from Sample Name 
```{r}
site<- sq %>%
  mutate(site = substr(sq$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)

@@

Add Dilution Column and Filter column
```{r}
dilution<- site%>%
  mutate(DIL = case_when(site == "BO"~"10",
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution))

@@

filter<- dilution %>%
   mutate(FIL = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt))

@@

Save as RDS and manually add date in excel
```{r}
write.csv(final, file= here("data","processed_data","vv_clean_copies.csv"))
write.csv(final_redo, file= here("data","processed_data","vv_clean_copies_redo.csv"))
```

>>>>

Create Site Column from Sample Name 
```{r}
site<- sq2 %>%
  mutate(site = substr(sq2$Sample,1,2)) #Creates new column `Site` from the first two letters in `Sample` (BO16 becomes BO)

@@

Add Dilution Column and Filter column
```{r}
dilution<- site%>%
  mutate(dilution = case_when(site == "BO"~"10",
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution))

@@

filter<- dilution %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt))

@@

Save as RDS and manually add date in excel
```{r}
#stop() #Write error so it wont overwrite
write.csv(final, file= here("data","processed_data","vv_clean_copies.csv"))
write.csv(final_redo, file= here("data","processed_data","vv_clean_copies_redo.csv"))
```
